A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-07 calculus.tex
Fix hboxes
Tables: caption above
Title case
Update results
small stuff

We introduce the two predicates that will be used by our calculus,
with the following definitions:
%
\begin{definition}\label{def:single-image}
  The Parikh predicate, $\SinglePredicateInstance$ holds for some
  automaton $\Automaton = \AutomatonTuple$, some map
  $\Map : \Alphabet^* \to \Monoid$ to a commutative monoid $\Monoid$,
  some transition selection function
  $\Filter:\: \Transitions \to \Naturals$, and some monoid
  element~$\MonoidElement \in \Monoid$ if $\MonoidElement$ is an
  element of the Parikh image of $\Language(\Automaton)$ modulo
  $\Map$, or more formally, when there is an accepting path
  $\Path = \PathEnumeration \in \Accepting{\Paths(\Automaton)}$ such
  that $\Filter(\Transition) = \TransitionCount(\Transition, \Path)$
  for all $t \in \Transitions$, and
  $\MonoidElement = \Map(\WordOf(\Path))$.
\end{definition}

@@

\begin{table}
\begin{tabular}{@{}l>{$}c<{$}p{3cm}@{}}\toprule
  Name & \text{Rule} & Side conditions\\
  \midrule

@@

  % SUBSUME
  \Subsume &
  \inferrule{\SomeInequalities,\SomeClause}{\Connected(\Automaton, \Filter), \SomeInequalities, \SomeClause} &
  \Split{} and \Propagate{}\newline cannot be applied \\
  \bottomrule
  \end{tabular}
  \caption{Derivation rules for one automaton.}\label{tbl:rules:single}
\end{table}

@@

\begin{figure}[h]

@@

  \infer1[\EquationReasoning: $=$-simplification]{

@@

  \infer1[\EquationReasoning{}: $=$-simplification]{

@@

\subsubsection{\Calculus{} terminates}
\begin{lemma}\label{lma:single-terminates}
  Suppose $\SomeClause{}$ is a set of formulas in which the predicates
  $\Image$ and $\Connected$ only occur positively. There is no
  infinite sequence of proofs~$P_0, P_1, P_2, \ldots$ in which $P_0$
  has $\SomeClause{}$ as root, and each $P_{i+1}$ is derived from
  $P_i$ by applying one of the rules in \cref{tbl:rules:single}.
\end{lemma}

@@

\subsubsection{The rules in \cref{tbl:rules:single} are solution-preserving}

>>>>

We introduce the two predicates that will be used by our calculus,
with the following definitions:
%
\begin{definition}\label{def:single-image}
  The Parikh predicate, $\SinglePredicateInstance$ holds for some
  automaton $\Automaton = \AutomatonTuple$, some homomorphism
  $\Map : \Alphabet^* \to \Monoid$ to a commutative monoid $\Monoid$,
  some transition selection function
  $\Filter:\: \Transitions \to \Naturals$, and some monoid
  element~$\MonoidElement \in \Monoid$ if $\MonoidElement$ is an
  element of the Parikh image of $\Language(\Automaton)$ modulo
  $\Map$, or more formally, when there is an accepting path
  $\Path = \PathEnumeration \in \Accepting{\Paths(\Automaton)}$ such
  that $\Filter(\Transition) = \TransitionCount(\Transition, \Path)$
  for all $t \in \Transitions$, and
  $\MonoidElement = \Map(\WordOf(\Path))$.
\end{definition}

@@

\begin{table}
  \caption{Derivation rules for one automaton.}\label{tbl:rules:single}
\begin{tabular}{@{}l>{$}c<{$}p{3cm}@{}}\toprule
  Name & \text{Rule} & Side conditions\\
  \midrule

@@

  % SUBSUME
  \Subsume &
  \inferrule{\SomeInequalities,\SomeClause}{\Connected(\Automaton, \Filter), \SomeInequalities, \SomeClause} &
  \Split{} and \Propagate{}\newline cannot be applied \\
  \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}[ht]

@@

  \infer1[\EquationReasoning: $=$-simp.]{

@@

  \infer1[\EquationReasoning{}: $=$-simp.]{

@@

\subsubsection{\Calculus{} Terminates}
\begin{lemma}\label{lma:single-terminates}
  Suppose $\SomeClause{}$ is a set of formulas in which the predicates
  $\Image$ and $\Connected$ only occur positively. There is no
  infinite sequence of proofs~$P_0, P_1, P_2, \ldots$ in which $P_0$
  has $\SomeClause{}$ as root, and each $P_{i+1}$ is derived from
  $P_i$ by applying one of the rules in \cref{tbl:rules:single}.
\end{lemma}

@@

\subsubsection{The Rules in \cref{tbl:rules:single} are Solution-preserving}
